---
title: "Emergency Department Patients"
author: "Callum Taylor"
date: "18 April 2017"
output: html_document
---

# Introduction

This document has two main parts.

This first part has a series of tables, one for each of the acute presentations and core presentations required for ACCS. Each table shows the relevant diagnoses for the presentation, with the amount of times I treated that diagnosis in the Emergency Medicine six month rotation.

The second part has a single table, with every diagnosis I made in the Emergency Medicine rotation, listed in order of frequency.

## Acute and Major Presentations

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(readxl)
library(stringr)
library(knitr)

# This imports all ED patients seen, and depersonalises their information
ed_logbook <- read_excel("patient_data/ED_Reviews.xls", col_names = TRUE) %>%
  select(-CHI, -Surname, -Forename)

# this imports all presentation codes for acute and major presentations
acute_presentation_codes <- tibble(
  title = c("Abdominal pain including loin pain",
            "Abdominal swelling mass and constipation",
            "Acute Back Pain",
            "Aggressive/Disturbed Behaviour",
            "Blackout/Collapse",
            "Breathlessness",
            "Chest Pain",
            "Confusion/Acute Delirium",
            "Cough",
            "Cyanosis",
            "Diarrhoea",
            "Dizziness and Vertigo",
            "Falls",
            "Fever",
            "Fits/Seizure",
            "Haematemisis/Malaena",
            "Headache",
            "Head Injury",
            "Jaundice",
            "Limb Pain (Atraumatic)",
            "Neck Pain",
            "Oliguric patient",
            "Pain Management",
            "Painful ears",
            "Palpitations",
            "Pelvic Pain",
            "Poisoning",
            "Rash",
            "Red Eye",
            "Mental Health",
            "Sore Throat",
            "Syncope/Presyncope",
            "Traumatic limb and joint injuries",
            "Vaginal Bleeding",
            "Ventilatory Support",
            "Vomiting and Nausea",
            "Weakness and paralysis", 
            "Wound assessment and management"
            ),
  category = c("AP"),
  code = 1:38
)

major_presentation_codes <- tibble(
  title = c("Anaphylaxis",
            "Cardio-respiratory arrest",
            "Major Trauma",
            "Septic patient",
            "Shocked patient",
            "Unconscious patient"
            ),
  category = c("CP"),
  code = 1:6
)

presentation_codes <- bind_rows(acute_presentation_codes, major_presentation_codes) %>%
  unite(presentation_code, category, code) %>%
  mutate(code_number = 1:44)


# this creates a list of words to get rid of from the presentation codes
filter_presentation <- tibble(
  word = c("patient", "including", "acute", "limb", "patient", "management", "red", "support", "assessment", "major", "injury", "traumatic", "respiratory")
)

altered_stop_words <- stop_words %>%
  filter(word != "back")

# this gives a list of all presentation codes
presentation_codes <- presentation_codes %>%
  group_by(presentation_code) %>%
  mutate(presentation_title = title) %>%
  unnest_tokens(word, title) %>%
  anti_join(altered_stop_words) %>%
  anti_join(filter_presentation)


# this gives a table listing all diagnoses made and their frequency of occurence
case_diagnoses <- ed_logbook %>%
  select(diagnosis = `Diagnosis Code`) %>%
  group_by(diagnosis) %>%
  count() %>%
  arrange(desc(n)) %>%
  filter(!is.na(diagnosis)) %>%
  mutate(diagnosis_code = diagnosis) %>%
  unnest_tokens(word, diagnosis) %>%
  anti_join(altered_stop_words) %>%
  distinct() %>%
  arrange(diagnosis_code)

# join all words

## this section connects cases and presentations by key words
## it then filters out pain management (pain and management both being words usually filtered out)
## it then removes pain from the rest of the words
## and puts pain management back in

all_joined <- presentation_codes %>%
  full_join(case_diagnoses, by="word")

pain_management <- all_joined %>%
  filter(presentation_code == "AP_23")

all_joined <- all_joined %>%
  filter(word != "pain") %>%
  bind_rows(pain_management)

presentations_with_diagnoses <- all_joined %>%
  filter(!is.na(diagnosis_code)) %>%
  filter(!is.na(presentation_title)) %>%
  select(-word)

presentations_table <- presentations_with_diagnoses %>%
  group_by(presentation_code, diagnosis_code) %>%
  distinct() %>%
  left_join(presentations_with_diagnoses, by = c("diagnosis_code", "presentation_code")) %>%
  select(code_number, presentation_code, presentation_title, diagnosis_code, n)

```

```{r remainder, include = FALSE, echo=FALSE}

# This section works out which acute/major presentations don't have a diagnosis
presentations_without_diagnoses <- all_joined %>%
  filter(is.na(diagnosis_code)) %>%
  filter(!is.na(presentation_title)) %>%
  select(presentation_code, presentation_title, code_number) %>%
  anti_join(presentations_with_diagnoses) %>%
  group_by(presentation_code, presentation_title, code_number) %>%
  distinct() %>%
  arrange(code_number)

# Then we take case diagnoses, including their number and their name, to export to edit
# When editing them we'll link diagnoses to the missing presentations, so every presentation has a valid diagnosis

diagnosis_numbers <- case_diagnoses %>%
  select(diagnosis_code, n) %>%
  group_by(diagnosis_code, n) %>%
  distinct() %>%
  arrange(diagnosis_code) %>%
  write_csv("diagnosis_numbers.csv")


# now what we'll want to do, is import our updated diagnoses back in
# then join them to case_diagnosis,
# then replay all_joined,
# then rebuild presentations_table

updated_diagnoses <- read_csv("updated_diagnosis_numbers.csv", col_names = TRUE)
case_diagnoses <- bind_rows(case_diagnoses, updated_diagnoses) %>%
  filter(!is.na(word))


all_joined <- presentation_codes %>%
  full_join(case_diagnoses, by="word")

pain_management <- all_joined %>%
  filter(presentation_code == "AP_23")

all_joined <- all_joined %>%
  filter(word != "pain") %>%
  bind_rows(pain_management)

presentations_with_diagnoses <- all_joined %>%
  filter(!is.na(diagnosis_code)) %>%
  filter(!is.na(presentation_title)) %>%
  select(-word)

presentations_table <- presentations_with_diagnoses %>%
  group_by(presentation_code, diagnosis_code) %>%
  distinct() %>%
  left_join(presentations_with_diagnoses, by = c("diagnosis_code", "presentation_code")) %>%
  select(code_number, presentation_code, presentation_title, diagnosis_code, n)


```


```{r tables, echo=FALSE, results='asis'}
for (i in 1:44){
  table_plot <- presentations_table %>%
    filter(code_number == i) %>%
    select(presentation_code, Diagnosis = diagnosis_code, `Number of patients` = n) %>%
    group_by(presentation_code, Diagnosis, `Number of patients`) %>%
    arrange(desc(`Number of patients`)) %>%
    distinct()
  
  count_caption <- table_plot %>%
    ungroup() %>%
    select(`Number of patients`) %>%
    sum() %>%
    as.character()
  
   name_caption <- presentations_table %>%
     filter(code_number == i) %>%
     ungroup() %>%
     select(presentation_title) %>%
     distinct %>%
     as.character()
   
   table_caption <- str_c(name_caption, ". Number of patients seen: ", count_caption)
  
  print(kable(table_plot, caption = table_caption))
}

```

## All diagnoses


```{r diagnoses, echo=FALSE, results='asis'}
diagnosis_numbers <- diagnosis_numbers %>%
  select(diagnosis = diagnosis_code, number = n) %>%
  group_by(diagnosis, number) %>%
  arrange(desc(number), diagnosis)

kable(diagnosis_numbers, caption = "All diagnoses made in the six month period")
```