---
title: "Intensive Care Medicine Patients and Procedures"
author: "Callum Taylor"
date: "17 April 2017"
output: html_document
---

# Introduction

This document has three main parts.

This first part has two tables, listing where a review I made for intensive care (or arrest/peri-arrest call I led) fitted as an acute or core major presentation

The second part has a single table, listing a proportion of the reviews and arrest/peri-arrest calls I attended in my 6 months of Intensive Care.

The third part is also a single table, listing the majority of the procedures I performed during my 6 months of Intensive Care

## Acute and Major Presentations

```{r setup, include=FALSE, message=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
procedures <- read_csv("logbook/CT2_ICM/Procedures.csv")
colnames(procedures)[1] <- "date"
procedures <- procedures %>%
  rename(procedure = Procedure, supervision = Supervision, sex=Gender, site=Site, uss = Ultrasound, vessel=Access)

procedures$date <- as.POSIXct(procedures$date)
procedures$procedure <- as.factor(procedures$procedure)
procedures$supervision <- as.factor(procedures$supervision)

reviews <- read_csv("logbook/CT2_ICM/Admissions.csv")
colnames(reviews)[1] <- "date"
reviews$Problem <- str_to_lower(reviews$Problem)

arrest_count <- str_sub(reviews$Problem, 1, 6)
arrest_count <- arrest_count == "arrest"
arrest_count <- sum(arrest_count, na.rm = TRUE)

# this imports all presentation codes for acute and major presentations
acute_presentation_codes <- tibble(
  title = c("Abdominal pain including loin pain",
            "Abdominal swelling mass and constipation",
            "Acute Back Pain",
            "Aggressive/Disturbed Behaviour",
            "Blackout/Collapse",
            "Breathlessness",
            "Chest Pain",
            "Confusion/Acute Delirium",
            "Cough",
            "Cyanosis",
            "Diarrhoea",
            "Dizziness and Vertigo",
            "Falls",
            "Fever",
            "Fits/Seizure",
            "Haematemisis/Malaena",
            "Headache",
            "Head Injury",
            "Jaundice",
            "Limb Pain (Atraumatic)",
            "Neck Pain",
            "Oliguric patient",
            "Pain Management",
            "Painful ears",
            "Palpitations",
            "Pelvic Pain",
            "Poisoning",
            "Rash",
            "Red Eye",
            "Mental Health",
            "Sore Throat",
            "Syncope/Presyncope",
            "Traumatic limb and joint injuries",
            "Vaginal Bleeding",
            "Ventilatory Support",
            "Vomiting and Nausea",
            "Weakness and paralysis", 
            "Wound assessment and management"
            ),
  category = c("AP"),
  code = 1:38,
  value = str_c(category, code)
)

major_presentation_codes <- tibble(
  title = c("Anaphylaxis",
            "Cardio-respiratory arrest",
            "Major Trauma",
            "Septic patient",
            "Shocked patient",
            "Unconscious patient"
            ),
  category = c("CMP"),
  code = 1:6,
  value = str_c(category, code)
)

presentation_codes <- bind_rows(acute_presentation_codes, major_presentation_codes) %>%
  unite(presentation_code, category, code) %>%
  mutate(code_number = 1:44)
```

```{r presentations, echo=FALSE, include=FALSE}
review_table <- reviews %>%
  filter(Role == "Reviewed") %>%
  select(Problem, Notes) %>%
  arrange(Problem) %>%
  rename(Codes = Notes)


codes <- review_table$Codes
codes <- str_split(codes, boundary("word"))
codes <- as_vector(codes)
codes <- as_tibble(codes)
codes$pres <- str_extract(codes$value, "[aA-zZ]+")
codes$num <- as.numeric(str_extract(codes$value, "[0-9]+"))

core_presentations <- codes %>%
  filter(pres == "CMP") %>%
  group_by(value, pres, num) %>%
  mutate(count = n()) %>%
  left_join(presentation_codes, by ="value") %>%
  select(code_number, presentation_code, title, num, count) %>%
  group_by(code_number, presentation_code, title, num, count) %>%
  distinct() %>%
  arrange(code_number) %>%
  ungroup() %>%
  select(presentation_code, title, count) %>%
  rename(`Number of Patients` = count)


acute_presentations <- codes %>%
  filter(pres == "AP") %>%
  group_by(value, pres, num) %>%
  mutate(count = n()) %>%
  left_join(presentation_codes, by ="value") %>%
  select(code_number, presentation_code, title, num, count) %>%
  group_by(code_number, presentation_code, title, num, count) %>%
  distinct() %>%
  arrange(code_number) %>%
  ungroup() %>%
  select(presentation_code, title, count) %>%
  rename(`Number of Patients` = count)
```

`r knitr::kable(core_presentations,caption="Core Major Presentations Covered By ICU Reviews", align = "l")`


`r knitr::kable(acute_presentations,caption="Acute Presentations Covered By ICU Reviews", align = "l")`


## Patient Reviews

```{r reviews, echo=FALSE}
knitr::kable(review_table,caption="ICU referrals/Peri arrest Calls reviewed during ICM")
```

## Procedures

```{r procedure_table, echo=FALSE}
table <- procedures %>%
  group_by(procedure) %>%
  count() %>%
  filter(procedure != "Peripheral venous access")
table$n[table$procedure == "Advanced Life Support (CPR)"] <- table$n[table$procedure == "Advanced Life Support (CPR)"] + arrest_count
```

```{r table, echo=FALSE}
knitr::kable(table,caption="Procedures performed during ICM")
```

